Toxic Code Snippets on Stack Overflow

### 2018-05-09 cloverflow-tse/cloverflow.tex
Fixed a small typo.
Added boxplots and table of clone size
Updated the boxplots and stats.
Updated the data after changing Bellon's ok-match threshold to 0.5. Now there are 2,289 clone pairs. Other stats are now updated to reflect the change.

	We surveyed 607 high reputation Stack Overflow users to study their
	awareness of the two issues.
\end{itemize}

@@

We selected the participants for our survey based on their Stack Overflow
reputation. On Stack Overflow, a user's reputation reflects how much the
community trust them. A user earns reputations when he or she receives up votes
for good questions and useful answers. Accepted answers receive more reputation
score than questions, and regular answers\footnote{Stack Overflow
Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site. In this study, we call Stack
Overflow users who have high reputation ``Stack Overflow answerers.''

@@

\begin{table}
	\caption{Investigated online clone pairs and corresponding snippets
		and Qualitas projects}
	\label{tab:snippets}
	\centering
	\begin{tabular}{p{2.2cm}rrrr}
		\toprule
		Set & Pairs & Snippets & Projects & Cloned ratio \\
		\midrule
		Reported clones & 2,302 & 460 & 59 & 53.10\% \\ 
		\midrule
		TP from manual validation & 2,076 & 443 & 59 & 53.89\% \\ 
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{table*}
	\centering
	\caption{Classifications of online clone pairs.}
	\label{tab:classification_good_o}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrrrrrrrr}
		\toprule
		Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
		\midrule
		Before consolidation & 248 & 1 & 199 & 107 & 1,505 & 16 & 226 & 2,302 \\
		After consolidation & 154 & 1 & 111 & 65 & 217 & 9 & 53 & 560 \\
		\bottomrule
	\end{tabular} 
	%}
\end{table*}

\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 248 online clone
pairs with evidence of cloning from Qualitas projects to Stack Overflow.
However, we observed that, in some cases, a cloned code snippet on Stack
Overflow matched with more than one code snippet in Qualitas projects because of
code cloning inside Qualitas projects themselves. To avoid double counting of
such online clones, we consolidated multiple clone pairs having the same Stack
Overflow snippet, starting line, and ending line into a single clone pair. We
finally obtained 154 QS pairs (\Cref{tab:classification_good_o}) having unique Stack Overflow code snippets and
associated with 23 Qualitas projects listed in \Cref{tab:qs_qualitas_projects}.
The most cloned project is \textsf{hibernate} with 24
clone pairs, followed by \textsf{eclipse} (21 pairs), \textsf{jung2} (19 pairs),
\textsf{spring} (17 pairs), and \textsf{jfreechart} (13 pairs). The clones are
used as examples and are very similar to their original Qualitas code with
limited modifications. Most of them have a statement in the Stack Overflow post
saying that the code is ``copied'', ``borrowed'' or ``modified'' from a specific
file or class in a Qualitas project. For example, according to the motivating
example in \Cref{fig:before-after}, we found evidence in the Stack Overflow Post
22315734 saying that \textit{``Actually, you can learn how to compare in Hadoop
from WritableComparator. Here is an examle that borrows some ideas from it.''}

\begin{table}
	\centering
	\caption{Qualitas projects associated with QS and UD online clone pairs}
	\label{tab:qs_qualitas_projects}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrlr}
		\toprule
		\multicolumn{2}{c}{QS} & \multicolumn{2}{c}{UD} \\
		\midrule
		Project & Pairs & Project & Pairs\\
		\midrule
		hibernate & 24 & netbeans & 11 \\
		eclipse & 21 & eclipse & 8 \\
		jung2 & 19 & jstock & 5 \\
		spring & 17 & compiere & 5 \\
		jfreechart & 13 & ireport & 4 \\
		hadoop & 10 & jmeter & 4 \\
		log4j & 8 & jung2 & 3 \\
		tomcat & 8 & jhotdraw & 3 \\
		struts & 5 & c-jdbc & 3 \\
		lucene & 4 & log4j & 3 \\
		weka & 4 & wct & 2 \\
		junit & 3 & hibernate & 2 \\
		poi & 3 & tomcat & 2 \\
		compiere & 2 & spring & 1 \\
		jasperreports & 2 & rssowl & 1 \\
		jboss & 2 & mvnforum & 1 \\
		jgraph & 2 & jfreechart & 1 \\
		jstock & 2 & jboss & 1 \\
		antlr & 1 & hadoop & 1 \\
		itext & 1 & geotools & 1 \\
		jgrapht & 1 & freemind & 1 \\
		ant & 1 & findbugs & 1 \\
		c-jdbc & 1 & cayenne & 1 \\
		\bottomrule
	\end{tabular} 
	%}
\end{table}

@@

\textbf{EX: External Sources.} We found 199 clone pairs from external sources to
Stack Overflow. After consolidating duplicated SO snippets due to multiple
intra-clone instances in Qualitas, we obtained 111 EX pairs. We found
evidence of copying from an external source to both Stack
Overflow and Qualitas in 50 pairs. Each of the pairs contains
statement(s) pointing to the original external location of the cloned
code in Qualitas and Stack Overflow. In addition, we found evidence
of copying from an external source to Stack Overflow, but not in
Qualitas, in 61 pairs. 
Our
analysis shows that the external sources fall into six groups as displayed in
\Cref{fig:ex_sources}. There are 63 EX online clone pairs copied
from source code of Java SDK (e.g.\ \textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}), 
18 pairs from websites, 15 pairs from open
source systems not in Qualitas (e.g.\ \textsf{Mozilla
	Rhino}), 11 pairs from Java official documentations from Sun
Microsystems or Oracle, 3 pairs from books, and 1 pair from a company
project. For example, Stack Overflow Post 9549009 contains a code comment saying
\textit{``Copied shamelessly from
	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''} which is an
open source project not included in the Qualitas corpus. Post 92962 includes a {\small\texttt{VerticalLabelUI}}
class with a license statement showing that it is developed by a private company
called \textsf{Sapient}. Post 12879764 has a text saying \textit{``Code modified
	and cleaned from the original at Filthy Rich Clients.''} which is a book for
developing animated and graphical effects for desktop Java applications. Another
example is a copy of code from a website in post 15260207. The text surrounding
source code reads ``\textit{I basically stole this from the web and modified it
	slightly... You can see the original post here
	(\url{http://www.java2s.com/Code/Java/Swing-JFC/DragListDemo.htm}).}''.
Interestingly, the code is actually a copy from Sun Microsystems.

>>>>

	We surveyed 201 high reputation Stack Overflow users to study their
	awareness of the two issues.
\end{itemize}

@@

We selected the participants for our survey based on their Stack Overflow
reputation. On Stack Overflow, a user's reputation reflects how much the
community trusts them. A user earns reputations when he or she receives up votes
for good questions and useful answers. Accepted answers receive more reputation
score than questions, and regular answers\footnote{Stack Overflow
Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site. In this study, we call Stack
Overflow users who have high reputation ``Stack Overflow answerers.''

@@

\begin{table}
	\caption{Investigated online clone pairs and corresponding snippets
		and Qualitas projects}
	\label{tab:snippets}
	\centering
	\begin{tabular}{p{2.2cm}rrrr}
		\toprule
		Set & Pairs & Snippets & Projects & Cloned ratio \\
		\midrule
		Reported clones & 2,289 & 460 & 59 & 53.28\% \\ 
		\midrule
		TP from manual validation & 2,063 & 443 & 59 & 54.09\% \\ 
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{table*}
	\centering
	\caption{Classifications of online clone pairs.}
	\label{tab:classification_good_o}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrrrrrrrr}
		\toprule
		Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
		\midrule
		Before consolidation & 247 & 1 & 197 & 107 & 1,495 & 16 & 226 & 2,289 \\
		After consolidation & 153 & 1 & 109 & 65 & 216 & 9 & 53 & 606 \\
		\bottomrule
	\end{tabular} 
	%}
\end{table*}

\begin{table}
	\centering
	\caption{Statistics of clone sizes}
	\label{tab:clone_stats}
	\begin{tabular}{lrrrr}
		\toprule
		Clones & Min & Max & Mean & Median \\
		\midrule
		QS & 10 & 135 & 18.6 & 14 \\
		SQ & 21 & 21 & 21.0 & 21 \\
		UD & 10 & 104 & 18.1 & 14 \\
		EX & 10 & 48 & 16.7 & 14 \\
		BP & 10 & 55 & 19.9 & 21 \\
		IN & 11 & 22 & 13.8 & 13.0 \\
		\bottomrule
	\end{tabular} 
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{boxplot_clone_size}
	\caption{Size of online code clones.}
	\label{fig:boxplotclonesize}
\end{figure}

\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 248 online clone
pairs with evidence of cloning from Qualitas projects to Stack Overflow.
However, we observed that, in some cases, a cloned code snippet on Stack
Overflow matched with more than one code snippet in Qualitas projects because of
code cloning inside Qualitas projects themselves. To avoid double counting of
such online clones, we consolidated multiple clone pairs having the same Stack
Overflow snippet, starting line, and ending line into a single clone pair. We
finally obtained 154 QS pairs (\Cref{tab:classification_good_o}) having unique Stack Overflow code snippets and
associated with 23 Qualitas projects listed in \Cref{tab:qs_qualitas_projects}.
The most cloned project is \textsf{hibernate} with 24
clone pairs, followed by \textsf{eclipse} (21 pairs), \textsf{jung2} (19 pairs),
\textsf{spring} (17 pairs), and \textsf{jfreechart} (13 pairs). The clones are
used as examples and are very similar to their original Qualitas code with
limited modifications. Most of them have a statement in the Stack Overflow post
saying that the code is ``copied'', ``borrowed'' or ``modified'' from a specific
file or class in a Qualitas project. For example, according to the motivating
example in \Cref{fig:before-after}, we found evidence in the Stack Overflow Post
22315734 saying that \textit{``Actually, you can learn how to compare in Hadoop
from WritableComparator. Here is an example that borrows some ideas from it.''}

\begin{table}
	\centering
	\caption{Qualitas projects associated with QS and UD online clone pairs}
	\label{tab:qs_qualitas_projects}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrlr}
		\toprule
		\multicolumn{2}{c}{QS} & \multicolumn{2}{c}{UD} \\
		\midrule
		Project & Pairs & Project & Pairs\\
		\midrule
		hibernate & 23 & netbeans & 11 \\
		eclipse & 21 & eclipse & 8 \\
		jung2 & 19 & jstock & 5 \\
		spring & 17 & compiere & 5 \\
		jfreechart & 13 & ireport & 4 \\
		hadoop & 10 & jmeter & 4 \\
		tomcat & 8 & jung2 & 3 \\
		log4j & 8 & jhotdraw & 3 \\
		struts2 & 5 & c-jdbc & 3 \\
		weka & 4 & log4j & 3 \\
		lucene & 4 & wct & 2 \\
		poi & 3 & hibernate & 2 \\
		junit & 3 & tomcat & 2 \\
		jstock & 2 & spring & 1 \\
		jgraph & 2 & rssowl & 1 \\
		jboss & 2 & mvnforum & 1 \\
		jasperreports & 2 & jfreechart & 1 \\
		compiere & 2 & jboss & 1 \\
		jgrapht & 1 & hadoop & 1 \\
		itext & 1 & geotools & 1 \\
		c-jdbc & 1 & freemind & 1 \\
		ant & 1 & findbugs & 1 \\
		antlr4 & 1 & cayenne & 1 \\
		\bottomrule
	\end{tabular} 
	%}
\end{table}

@@

\textbf{EX: External Sources.} We found 197 clone pairs from external sources to
Stack Overflow. After consolidating duplicated SO snippets due to multiple
intra-clone instances in Qualitas, we obtained 109 EX pairs. We found
evidence of copying from an external source to both Stack
Overflow and Qualitas in 49 pairs. Each of the pairs contains
statement(s) pointing to the original external location of the cloned
code in Qualitas and Stack Overflow. In addition, we found evidence
of copying from an external source to Stack Overflow, but not in
Qualitas, in 60 pairs. 
Our
analysis shows that the external sources fall into six groups as displayed in
\Cref{fig:ex_sources}. There are 63 EX online clone pairs copied
from source code of Java SDK (e.g.\ \textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}), 
18 pairs from websites, 14 pairs from open
source systems not in Qualitas (e.g.\ \textsf{Mozilla
	Rhino}), 10 pairs from Java official documentations from Sun
Microsystems or Oracle, 3 pairs from books, and 1 pair from a company
project. For example, Stack Overflow Post 9549009 contains a code comment saying
\textit{``Copied shamelessly from
	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''} which is an
open source project not included in the Qualitas corpus. Post 92962 includes a {\small\texttt{VerticalLabelUI}}
class with a license statement showing that it is developed by a private company
called \textsf{Sapient}. Post 12879764 has a text saying \textit{``Code modified
	and cleaned from the original at Filthy Rich Clients.''} which is a book for
developing animated and graphical effects for desktop Java applications. Another
example is a copy of code from a website in post 15260207. The text surrounding
source code reads ``\textit{I basically stole this from the web and modified it
	slightly... You can see the original post here
	(\url{http://www.java2s.com/Code/Java/Swing-JFC/DragListDemo.htm}).}''.
Interestingly, the code is actually a copy from Sun Microsystems.
